# General Discussion {#general-discussion}

```{r, include=FALSE}
# all that needs to be changed is seq_id in the run_autonum function, which restarts figure/table numbering with each chapter

# create functions for table and figure captions using officer functions

# these functions use the chunk label to enable cross-referencing with bookdown syntax 

table_caption <- function(caption){
  block_caption(label = caption,
              style = "Table Caption",
              autonum = run_autonum(seq_id = "chp6tab", 
                       pre_label = "Table ", 
                       tnd = 1, tns = ".", 
                       bkm = opts_current$get("label"),
                       prop = fp_text_lite(bold = TRUE)))
}

figure_caption <- function(caption){
  block_caption(label = caption,
              style = "Image Caption",
              autonum = run_autonum(seq_id = "chp6fig", 
                       pre_label = "Figure ", 
                       tnd = 1, tns = ".", 
                       bkm = opts_current$get("label"),
                       prop = fp_text_lite(bold = TRUE)))
}

# an alternative to include_graphics - figures are in their original aspect ratio (but huge in the output, usually like 200% so I might have to manually go in and change everything...)

officer_figure <- function(file){
fpar(external_img(file, guess_size = T), fp_p = fp_par_lite(word_style = "Figure", keep_with_next = T))
}
```

## Results Summary {#discussion-results-summary}

<!-- this is all I'm gonna do for this summary -->

In this dissertation, I explored the relationship between gradient categorization, linguistic diversity, and the acquisition of L2 phonemic contrasts combining existing and novel methods to measure L1 and L2 speech perception, experiential and manipulated linguistic diversity, and L2 perceptual discrimination and listening accuracy. Table \@ref(tab:rq-summary) summarizes the specific relationships investigated in the present study in the context of the specific aims and research questions.

```{r label="rq-summary", tab.id="rq-summary"}
#officer_figure("table/ft-rq-summary.png")

table_caption("Summary of the Predictors, Effects, and Outcome Variables of Interest in the Context of the Specific Aims and Research Questions.")
st3e$ft.rq.summary
```

The relationship between linguistic diversity (LD), L1 and L2 gradient categorization, and L2 speech learning was explored at various combinations of LD as a predictor/effect, L1 and L2 categorization measures as both outcome variables and predictor variables, and L2 speech learning as outcome variables. With regards to linguistic diversity (LD) as a predictor and an effect on categorization measures, experiential LD was not found to predict L1 and L2 gradient categorization or secondary cue use (RQ1), and there was no significant evidence found for the effect of training with specific LD on L1 and L2 gradient categorization (RQ2). In fact, across Studies 2 and 3, the VAS measures of slope and response variability did not significantly change from pretraining to posttraining, in either cases of short-term or long-term training. As predictor variables for secondary cue use and L2 speech learning, L1 and L2 gradient categorization measures were not consistently found to predict L1 and L2 secondary cue use (RQ1), nor L2 discrimination ability (RQ2), nor L2 listening accuracy (RQ3). With regards to LD as an effect on L2 speech learning, short-term perceptual training led to improvements in L2 discrimination ability for naïve monolingual listeners, however, specific LD was not found to have an effect on the magnitude of learning gains (RQ2). There was no significant evidence found for the effect of long-term perceptual training, with or without specific LD, on L2 discrimination ability (RQ2) nor L2 listening accuracy (RQ3) for L2 learners in Japanese language classrooms. The following sections explore the implications of these findings, and lack of findings, on the relationship between these three factors in the context of extant literature.

## Implications {#discussion-implications}

<!-- okay done -->

### Gradient categorization and linguistic diversity {#discussion-gradiency-and-LD}

<!-- done -->

#### Categorization gradiency {#discussion-categorization-gradiency}

<!-- done -->

In Study 1, experiential LD, measured as two indices of multilingual language diversity (MLD), was not found to predict L1 or L2 categorization gradiency, response variability, or secondary cue use. To my knowledge, this dissertation is the first study to use MLD, which is a form of language entropy, to predict gradient measures of categorization. The study from @Kutlu2024Social, one of the studies with the key findings that motivated the hypotheses of this dissertation, had found that linguistic diversity predicted gradient response profiles in children using social network analysis, and linguistic diversity was operationalized as the number of individuals who speak a different language/dialect out of the total network size. It is possible that the difference between operationalizing LD as language entropy vs. social network diversity led to the difference in results.

Previous research that operationalized LD using forms of language entropy have found that LD is associated with particular patterns of neural connectivity and behaviors of domain-general executive control. For example, high social LD has consistently been found to be associated with increased structural connectivity between a diverse set of brain regions implicated in non-inhibition-related domain-general executive functions, as opposed to domain-specific language-related regions, including language- and task-switching, and proactive executive control [@Gullifer2018Bilingual; @Sulpizio2020Bilingualism]. This modulatory effect of LD on neural connectivity was additionally found in behavioral measures of increased efficiency of L1 production in the face of increasing task demands [@Kang2023Multilingual], and faster RTs in conflict-monitoring, task-switching, and goal maintenance behaviors [@Li2021Bilingual].

On the other hand, previous studies sought to connect VAS-measured categorization gradiency with measures of executive functioning and found an association between gradient categorization and working memory [@Kapnoula2017Evaluating; @Kim2020Individual]. These studies notably did not find an association between gradiency and other executive function behaviors measured, including task-switching, cognitive control, and inhibitory control [@Kong2016Individual; @Kapnoula2017Evaluating; @Kim2020Individual; cf. @Kapnoula2021Idiosyncratic who did find an association between gradiency and inhibitory control].

The findings of the present study may raise questions about the sensitivity of MLD as a predictor of categorization gradiency, but the literature linking both LD and gradiency to executive function offers an alternative explanation. The lack of overlap between the executive functions associated with LD and gradiency may point to the fact that the effect of LD on neural connectivity does not extend to the mechanisms involved in perceptual categorization. Notably, the study by @Li2021Bilingual included the finding that those with high LD experienced more conflict in inhibitory control behaviors. A seemingly unrelated finding from @Kim2020Individual suggested that inhibitory control was linked to short-term perceptual adaptability, but not working memory, which was found to be associated with gradiency. @Kim2020Individual suggested the explanation that “different cognitive abilities may underlie gradiency and adaptation in speech perception” (p. 14). Indeed, taking these results together, it is possible that the cognitive abilities that underlie gradiency are unrelated to the cognitive abilities found to be associated with LD.

#### Secondary cue use {#discussion-secondary-cue-use}

<!-- done -->

Study 1 also did not find evidence that gradiency predicted L1 or L2 secondary cue use. The lack of effect between L1 gradiency and L1 secondary cue use does not align with previous findings that established this association [@Kong2016Individual; @Kapnoula2017Evaluating; @Kapnoula2021Gradient; @Kapnoula2021Idiosyncratic; @Kim2020Individual]. There are a few key differences between the listed studies and the present study. First, excluding the early study from @Kong2016Individual, these studies all used the rotated logistic function to estimate measures of categorization, including the estimation of the theta angle representing relative secondary cue use. However, only one study used theta in the subsequent statistical analyses link gradiency and secondary cue use [@Kapnoula2021Idiosyncratic]. The other studies used crossover difference between 2AFC response curves at different steps of the secondary dimension as the measure of secondary cue use. Second, these studies all used secondary cue use to predict categorization gradiency, meaning secondary cue use was included as an independent variable in models with VAS slope as the dependent variable, or used correlation analyses. As previous findings of this association have not been consistent across contrasts [@Kapnoula2021Gradient; @Kapnoula2021Idiosyncratic]; @Kapnoula2021Idiosyncratic suggested that contrary to the assumptions from the earlier findings, "cue integration [may be] a consequence rather than a source of gradiency" (p. 16). It was for this reason I used the gradiency measures as independent variables in models with secondary cue use as the dependent variable, to assess the degree to which gradiency predicted secondary cue use. The results from this analysis suggested that gradiency cannot be used to predict secondary cue usage in the same way secondary cue usage has been used to predict gradiency, as in previous literature.

#### Individual differences in gradient categorization and secondary cue use {#discussion-individual-differences}

<!-- done here -->

A consistent finding from the present research was the considerable individual variability in categorization gradiency, response variability, and secondary cue use. Although these individual differences were not systematically predicted by linguistic diversity, experiential or specific, these findings contribute to the growing consensus that categorization is not a unitary skill but a process that brings together multiple mechanisms. These three factors of gradiency, response variability, and secondary cue use reflect subprocesses that vary not only according to the individual, but also to context- and phoneme-specific demands. In fact, it may be the case that the three factors reflect processes at different organizational stages of the speech perception process in line with the three distinct speech processing strategies suggested by @Werker1985Crosslanguage. In their study, they found evidence that participants could "(1) classify the syllables according to familiar phonemic categories, (2) show a perceptual sensitivity to nonnative, phonetically relevant category boundaries, and (3) discriminate syllables on the basis of any acoustic variability between individual exemplars" (p.43), which provided supported for the hypotheses of distinct processes (1) phonemic perception, (2) intermediate-level phonetic perception, and (3) auditory perception. As such, individual-, language-, and contrast-level differences in categorization and the difficulty in finding a systematic connection predicting each factor may suggest that each of the three processes are more distinct that previously hypothesized. It could be the case that, for example, response variability reflects processes at the level of (1) phonemic perception, by reflecting the noisiness of phonological representations [@Fuhrmeister2021Structural], secondary cue use reflects processes at the level of (2) phonetic perception, by reflecting how the perceptual system organizes the relationship between acoustic cues and speech categories [@Kapnoula2021Gradient], and gradiency reflects processes at the level of (3) auditory perception, by reflecting how the auditory system faithfully encodes continuous acoustic information [@Ou2022Neural]. The distinction of the processes reflected by these three measures may thus explain not only the variability across individuals, but the variability within individuals seen within and across the L1 and L2 contrast pairs. Future research may wish to use more fine-grained measurements, such as neuroimaging, to explore how the VAS measures each distinctly connect to phonological representations, perceptual organization, and encoding strategies, and how these differ between the perception of L1 and L2 speech.

### Gradient categorization, specific LD, and L2 phoneme acquisition {#discussion-gradiency-LD-and-L2}

<!-- good enough -->

In Studies 2 and 3, the manipulation of specific LD via perceptual training was not found to have a consistent effect on L1 or L2 categorization gradiency or response variability. Along with the findings from Study 1 that MLD did not predict measures of gradient categorization, this may reflect that gradiency and response variability are relatively stable traits that are not so easily malleable to the effects of perceptual training. At first glance, this may appear to contradict the wealth of literature showing evidence that humans are capable of rapid perceptual adaptation and acoustic cue-reweighting after exposure to short-term speech regularities, such as those introduced by artificial accents [e.g., @Idemaru2011Word; @Idemaru2014Specificity; @Reinisch2014Phonetic; @Lehet2017DimensionBased; @Lehet2020Nevertheless; @Idemaru2020Generalization]. However, the idea that measures of gradient categorization are robust against perceptual learning aligns with the findings from @Kim2020Individual, who suggested that perceptual adaptation and perceptual categorization rely on different cognitive mechanisms, despite the fact that both processes involve the mapping of acoustic cues to phoneme categories. In fact, there is evidence that the gradiency of category representations develops over the course of years through adolescence [@McMurray2018Speech]. Combined with the report from @Kong2016Individual that participants' VAS response patterns were consistent across two sessions separated by one week, the findings from the present study showing stability in VAS measures across 24 hours and across several weeks lend support to the idea that categorization patterns, while phoneme-specific, are stable within individuals across time.

Another goal of this dissertation, framed in the second part of RQ2, was to determine whether gradient categorization might mediate the effect of specific LD on successful L2 learning, however, neither L1 or L2 gradiency or response variability predicted changes in L2 discrimination sensitivity or L2 listening accuracy. The lack of predictive effect of gradiency is consistent with a few studies that have explored the relationship between gradiency and L2 perception and learning [@Honda2024Exploring; @Fuhrmeister2023Relationships], although is inconsistent with other studies that did find that gradiency predicted L2 learning performance [@Lee2024Acoustic] or reported L2 proficiency [@Kapnoula2024Sensitivity; @Kong2023Individual]. Further, the lack of predictive effect of response variability contradicts the findings from @Honda2024Exploring and @Fuhrmeister2023Relationships, who both showed that categorization consistency, rather than gradiency, predicted better performance in non-L1 speech perception. Here too, the inconsistency in findings among previous literature and the present study may lie in the difference in operationalization of measures for L2 learning and L2 proficiency.

### Linguistic diversity and L2 phoneme acquisition {#discussion-LD-and-L2}

<!-- good enough -->

#### Implications for specific LD via perceptual training

<!-- good enough -->

The manipulation of specific LD via perceptual training did not lead to differential learning results among the training groups. One possibility is that the scaling of LD in this study was insufficient and that exposing learners to just one additional language may not approximate the effects of specific linguistic diversity observed in other studies [e.g., @Wiener2019Second]. On the other hand, previous research has often found no additional advantage in trilinguals over bilinguals [e.g., @Werker1986effect; @Patihis2015Phoneme], so it is possible increasing the number of training languages would not affect the results. Additionally, despite the evidence showing the benefits of specific language knowledge in the learning of specific L2 contrasts [@Wiener2019Second; @Patihis2015Phoneme; @Pajak2014role], other research has found evidence suggesting the opposite, that there is no difference in benefit between those who have specific and non-specific multilingual language experience [e.g., @Enomoto1994L2], which aligns with the results of Study 2.

Another possibility is that the duration of exposure to specific LD was just too limited to contribute to learning, even though learning did occur. The both the short-term and long-term training sessions were not as immersive or long enough to approximate the long-term effects of linguistic diversity observed in other studies [e.g., @Bice2019English]. It may also be the case that the effects of specific LD occurred at a level not measured, for example, at the level of neural patterns or structures. For example, the effects of environmental linguistic diversity [@Bice2019English] and passive laboratory exposure to an unknown language [@Kurkela2019Passive; @Gullberg2010Adult] were found to result in changes in neural patterns measured by ERPs or structural neural connectivity found using neuroimaging, but not in the behavioral measures employed by this study.

Notably, despite the lack of differential learning effects from specific LD, improved discrimination sensitivity was observed for the naïve monolingual listeners but not for the L2 Japanese classroom learners. The finding with the naïve monolingual listeners is consistent with the vast amount of literature showing that even short-term perceptual training can lead to gains in non-L1 perceptual sensitivity [e.g., @Logan1991Training, Lively1993Training; @Iverson2005Phonetic; @Iverson2012Auditory], which has also been replicated in the literature examining non-L1 learning of Japanese length contrasts with varying effect sizes [e.g., @Tajima2003Perception; @Hirata2004Training; @Hirata2007Training].

However, the lack of training effects for L2 Japanese classroom learners contradicts existing literature that learners with experience in the L2, including classroom experience, show learning gains from perceptual training [e.g., @Motohashi-Saigo2009Acquisition; @Hirata2004Computer; @Sonu2013Nonnative; @Georgiou2021Effects; @Tajima2003Perception]. The null finding is more likely to reflect the limitations of Study 3 from the small sample sizes rather than a true null effect. Further, Study 3 was also limited due to the heterogeneity among experimental groups at baseline measurements.

#### Implications for experiential LD

<!-- good enough for right now -->

Although neither MLD nor specific LD as a manipulation were found to predict or have an effect on the L2 learning measurements, this dissertation presents a preliminary step in characterizing a facet of multilingualism, that is, passive or indirect exposure to LD, that is not often quantitatively operationalized and not often connected with perceptual behaviors. Besides @Kutlu2024Social, who offered a quantitative measure of LD using social network analysis, other studies linking environmental or ambient linguistic diversity to language processing and learning either binned groups categorically [@Bice2019English] or did not compare the population of study to populations in environments with low linguistic diversity [@Oh2020NonMaorispeaking; @Todd2023Language]. Additionally, to the best of my knowledge, this dissertation is the first study connecting LD using language entropy to L2 categorization and learning.

A wealth of prior literature has provided evidence for the various benefits of exposure to LD. Critically, however, these studies all examine the effects of LD in children or effects from exposure to LD during childhood, and this includes the study from @Kutlu2024Social. For example, monolingual children exposed to LD from their social network, classroom, or neighborhood environment were found perform better than purely monolingual children, and sometimes just as well as multilingual children, in areas such as cognitive abilities [@Tsimpli2020Linguistic], effective communication [@Fan2015Exposure], reading comprehension [@Dotzel2021impact], learning foreign labels [@Akhtar2012Learning], and social learning for infants [@Howard2014Neighborhood]. The effects of childhood exposure to LD have been found even in adults. Specifically, adults who had minimal experience with [@Au2008Salvaging] or frequently overheard [@Au2002Overhearing; @Knightly2003Production] Spanish during their childhood had a pronunciation advantage when learning Spanish as adults compared to those with no regular experience with Spanish until later in their adolescence.

These studies all seem to suggest that learning benefits from exposure to LD stem from childhood exposure, which may indicate that LD influences cognitive behavior at a developmental trajectory spanning years. The amount of exposure to LD during the training paradigms employed in the present study, which were only on the time scale of hours in total, were likely not enough to induce the degree of perceptual benefits of LD that was seen in prior literature.

Despite this, the benefits of LD, even if limited to early development exposure, cannot be understated. Future research may wish instead to focus on producing early-childhood multilingual interventions [e.g., @Festman2018Vocabulary; @VanLaere2017What] and encouraging out-of-school exposure to LD [e.g., @Wilde2020Learning], or alternatively, to investigate long-term late exposure interventions to replicate the effects of childhood exposure to LD.

## Limitations and Future Directions {#future-directions}

<!-- done -->

There were several limitations that constrained the interpretability and generalizability of the findings. The studies were primarily limited by small sample sizes, insufficient training time, and the choice of statistical analyses. As a result, the study instruments may not have been tuned or sensitive enough to measure the constructs of interest, namely, passive MLD, the implementation of specific LD in the training paradigm, and L2 listening. Future research should build on these foundations by addressing the following areas.

**Experiential LD**: Future work should prioritize validation of the LDQ. Language entropy itself has been validated as a measure of linguistic diversity [@Gullifer2020Characterizing; @Gullifer2021Bilingual], so validation should focus on the construct validity of the Part 2 questionnaire items. Construct validity might be assessed using factor analysis and measures of test-retest reliability [e.g., @Anderson2018language; @Aparici2024Multilingual; @Mann2022Bilingual; @Kalamala2023Bilingualism]. Additionally, to confirm construct validity, questionnaire items may be compared to other, more objective measures of passive language use an exposure, such as measures from language use logs [e.g., @Alvarez2020Measuring] and social media use [e.g., @Zhuravleva2016Using]. Further, future researchers may wish to incorporate social network analysis [e.g., @Kutlu2024Social; @Tiv2022Bridging] and measures of sociolinguistic context [e.g., @Wigdorowitz2022Sociolinguistic; @Wigdorowitz2023holistic] to flesh out the construct of experiential linguistic diversity. The steps outlined in @ArtinoJr.2014Developing and @Boateng2018Best are further recommended for questionnaire development, with @Haukas2021Developing serving as a good example of questionnaire development and validation with regards to multilingualism.

**Training with LD**: For future studies interested in using LD in a perceptual training paradigm, the research would benefit from expanding the diversity and ecological validity of the multilingual training input. For one, extending the duration of training to a semester-long intervention, or longer, would better approximate the long-term nature of exposure that likely underpins the benefits of childhood exposure to LD. Further, future work could add additional languages to the stimulus set and use natural language input rather than isolated minimal pairs. This may look like using carrier sentences for the training items, or increasing the complexity of the training items from words in isolation to semantically meaningful carrier sentences, a training paradigm introduced and implemented successfully by @Hirata2004Computer. Several previous studies have used computer-assisted language learning (CALL) technology to translate perceptual training paradigms to L2 classroom tools, all of which offer guidelines and serve as examples in making adaptive, multimodal, and engaging tools that make use of minimal pairs to improve both perception and production/pronunciation [@Tejedor-Garcia2020Assessing; @Zhang2023Using; @Qian2018system]. 

As for using more languages to diversify the stimulus set, in the case of Japanese vowel length and consonant gemination, other languages besides MSA that feature length contrasts that are independent between vowels and consonants include Hungarian, Malayalam, Tamil, and Finnish. The use of minimal pairs, while simple in theory, does pose a difficulty, especially for low resource languages. Instructors may find the search for suitable minimal pairs depending on the target language and target phonemic contrasts to be prohibitive. A few researchers have begun to develop methods and tools to source minimal pairs for language teaching purposes [@Levis2008Minimal; @Qian2015Extracting; @Mairano2016Are], although this is another area of research that should be expanded. 

**Measures of L2 learning and categorization**: Further validation of the MCPD task is needed, especially in comparison with other measures of L2 listening. Despite the null results of the current study, the VAS task remains a promising and well supported instrument for capturing gradient categorization and should continue to be used in increasing diverse phonemic and linguistic contexts. To capture categorization effects that may not be observable from behavioral measures, future research should incorporate neuroimaging measures. Using the work showing the structural connectivity associated with language entropy [@DeLuca2019Redefining; @Gullifer2018Bilingual; @Li2021Bilingual; @Sulpizio2020Bilingualism] and the work mapping the neural correlates of gradient categorization [@Fuhrmeister2021Structural; @Ou2022Neural], future work may aim to uncover structural or functional bridges between these two constructs. If such bridges are found, they could pave the way for more targeted interventions that leverage these structural differences for the benefit of L2 learning.

## Conclusion {#conclusion}

<!-- okay done -->

Overall, this dissertation made several theoretical, methodological, and applied contributions to the field of applied psycholinguistics and second language acquisition. As a theoretical contribution, this dissertation aimed to investigate the role of linguistic diversity in L2 speech learning, and whether gradient categorization is the perceptual mechanism that connects the two constructs. Not only that, but the research also attempted to elucidate whether linguistic diversity, as measured by language entropy, is a contributing factor to the individual differences found in speech categorization patterns. While the findings did not align with my hypothesis, the data contribute to the growing discussion around the gradient categorization theoretical framework by expanding the conversation to L2 speech contrasts and the impact of categorization patterns on L2 speech learning. The findings serve as a starting point for future studies to further investigate the sources of individual differences in speech categorization and the effect of these differences on speech category learning.

In terms of methodological contributions, through this research project, I developing new measurement tools and expanding existing paradigms. First, I created a new questionnaire to quantify experiential linguistic diversity for passive language use and exposure using language entropy. Second, I incorporated linguistic diversity as a novel manipulation to an existing perceptual training paradigm. Third, I developed a short, ecologically-relevant listening assessment task to assess L2 perception and listening accuracy of more naturalistic speech stimuli. These methodologies, and the findings with regards to perceptual learning, provide an applied contribution by highlighting the role of perceptual training and its possible use cases in the L2 classroom setting, especially as a learning tool focused on phonemic contrasts to supplement classroom instruction. In closing, this dissertation presents meaningful starting points for future studies interested in connecting gradient speech categorization, linguistic diversity, and L2 speech learning.
